Paper 1

### 2022-05-29 scripts/Paper 1.Rmd
update

@@

```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("month", "Year"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

input.daily %>% select(jday, NEE_LT.gC, Year) %>%
  ggplot(., aes(jday, NEE_LT.gC)) +
  geom_line(aes(colour = Year))

NEE.summary %>%
  ggplot(., aes(jday, seasonal.sum)) +
  geom_line(aes(colour = Year))

>>>>

rainfall%>% ddply(c("Year", "season"), summarise,
                    seasonal.sum = sum(Precip, na.rm = TRUE))

@@

```{r seasonal NEE}
NEE.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(NEE_LT.gC))

GPP.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))

ER.summary <- input.daily %>% ddply(c("Year", "month"), summarise,
                                       monthly.sum = sum(ER_LT.gC))

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly NEE")+
  xlab("month")+
  theme_classic()

GPP.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly GPP")+
  xlab("month")+
  theme_classic()

ER.summary %>%
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly ER")+
  xlab("month")+
  theme_classic()
```
